\href{https://travis-ci.org/aracelis-git/Midterm_project}{\tt !\mbox{[}Build Status\mbox{]}(https\-://travis-\/ci.\-org/aracelis-\/git/\-Midterm\-\_\-project.\-svg?branch=master)} 



\subsection*{Overview and Purpose}

Originally made to create a self-\/learning tic-\/tac-\/toe robot.

The final product is a tic-\/tac-\/toe game played within the command line against another person.

The execution of the program is relatively easy. Execute the tictactoe.\-exe, then press any number from 1-\/9 to indicate your choice of move. 1 is the top left corner, 2 being the top position, and continues onwards with a top to bottom, left to right scheme. \char`\"{}\-O\char`\"{} and \char`\"{}\-X\char`\"{} take turns with \char`\"{}\-O\char`\"{} starting first.

\subsection*{License}

Copyright 2017 Aldrin I. Racelis

Licensed under the Apache License, Version 2.\-0 (the \char`\"{}\-License\char`\"{}); you may not use this file except in compliance with the License. You may obtain a copy of the License at

\href{http://www.apache.org/licenses/LICENSE-2.0}{\tt http\-://www.\-apache.\-org/licenses/\-L\-I\-C\-E\-N\-S\-E-\/2.\-0}

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an \char`\"{}\-A\-S I\-S\char`\"{} B\-A\-S\-I\-S, W\-I\-T\-H\-O\-U\-T W\-A\-R\-R\-A\-N\-T\-I\-E\-S O\-R C\-O\-N\-D\-I\-T\-I\-O\-N\-S O\-F A\-N\-Y K\-I\-N\-D, either express or implied. See the License for the specific language governing permissions and limitations under the License.

\subsection*{Dependencies}

No Dependencies

\subsection*{Build}

After cloning the repository, build the file using cmake and make.

mkdir build cd build cmake .. make

\subsection*{Demo}

Below is a video of the game in action.

\href{https://drive.google.com/open?id=0BxfrmvtnmsrXdmNpLXRlMXR1T3M}{\tt Link to the Demo video}

To run the game yourself, follow the instructions for build, then in the same folder, run the following code.

./app/tictactoegame

\subsection*{S\-I\-P}

\href{https://drive.google.com/open?id=1KFQ9Ns8AJOG_RbMY5DaGz2tUdGVuaAmlSZTdXr1TY-M}{\tt Backlog} \href{https://docs.google.com/spreadsheets/d/1cvphMVsGHO1l1VFnBONkp5L9tVWFDhlSldkhnq5PvsM/edit?usp=sharing}{\tt Product Log}

\subsection*{Tests}

Unit tests made with gtest verfied the functions of both the game and game\-Board classes. To run the test, execute the following code in the root directory.

mkdir build cd build cmake .. make test/cpp-\/test

The unit tests are integrated with Travis, as seen by the badge at the top of the readme.

\subsection*{Doxygen Generation}

I generated the documents using the following commands within the command line\-:

doxygen -\/g doxygenfile

doxygen doxygenfile 